Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)

### 2015-03-02 tuningpredictor.tex
update
safety save

 \setlength{\floatsep}{1ex}
 \setlength{\textfloatsep}{1ex}
\usepackage[compact,small]{titlesec}
\DeclareMathSizes{7}{7}{7}{7} 
\pagenumbering{arabic}
\setlength{\columnsep}{7mm}

@@

@@

%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
\renewcommand\arraystretch{1.2}
\begin{figure*}[t!]
\scriptsize
  \centering
	\begin{tabular}{|c|c|c|c|l|}
	\cline{1-5}
	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
\multicolumn{1}{c|}{Description} \\ \hline
	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
	& infogain & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
one is for clustering and the second one is building prediction model. we explicitly call Where-
clustering tree and CART tree, respectively}. \\ \cline{2-5} 
	 & min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
CART tree. \\ \cline{2-5} 
	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
\end{tabular} \\ \cline{2-5} 
    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
clustering tree. \\ \cline{2-5} 
	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
\hline
\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
split. \\ \cline{2-5}

@@

%%%%parameters for pd %%%%%%
\begin{figure*}[!ht]
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.17& 0.17& 0.02& 0.04& 0.42& 0.7& 0.8& 0.25& 0.32& 0.13& 0.61& 0.77& 0.09& 0.02& 0.68& 0.17& 0.01\\ \cline{2-20}
& infoPrune& 0.33& 0.13& 0.06& 0.12& 0.35& 0.44& 0.26& 0.33& 0.81& 0.03& 0.32& 0.89& 0.05& 0.1& 0.97& 0.15& 0.24& 0.01\\ \cline{2-20}
& min\_sample\_size& 4& 5& 2& 4& 1& 7& 6& 9& 6& 9& 8& 1& 3& 3& 9& 5& 4& 2\\ \cline{2-20}
& min\_Size& 0.5& 0.49& 0.24& 0.41& 0.26& 0.12& 0.03& 0.26& 0.06& 0.19& 0.38& 0.02& 0.07& 0.2& 0.2& 0.32& 0.13& 0.86\\ \cline{2-20}
& wriggle& 0.2& 0.65& 0.19& 0.42& 0.37& 0.22& 0.56& 0.64& 0.26& 0.79& 0.97& 0.23& 0.52& 0.99& 0.78& 0.15& 0.58& 0.55\\ \cline{2-20}
& depthMin& 2& 4& 3& 2& 5& 5& 4& 3& 5& 4& 4& 2& 4& 2& 1& 4& 3& 1\\ \cline{2-20}
& depthMax& 10& 16& 7& 19& 11& 14& 16& 12& 12& 19& 17& 12& 13& 15& 13& 3& 17& 15\\ \cline{2-20}
& wherePrune& False& True& False& False& False& False& False& False& True& True& False& False& True& False& True& False& False& False\\ \cline{2-20}
& treePrune& True& True& True& True& False& False& False& False& False& True& True& False& False& True& False& False& True& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.01& 0.13& 0.01& 0.01& 0.06& 0.34& 0.01& 0.15& 0.39& 0.01& 0.05& 0.06& 0.01& 0.01& 0.18& 0.06& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.9& 0.01& 0.01& 0.45& 0.14& 0.52& 0.57& 0.76& 1& 0.68& 0.01& 0.33& 0.01& 0.73& 0.04& 0.01\\ \cline{2-20}
& min\_samples\_split& 2& 17& 20& 7& 18& 9& 11& 15& 16& 12& 11& 2& 6& 3& 13& 19& 13& 10\\ \cline{2-20}
& min\_samples\_leaf& 1& 11& 1& 9& 2& 19& 14& 6& 15& 4& 17& 19& 9& 12& 5& 4& 7& 13\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.09& 0.01& 0.01& 0.01& 0.36& 0.49& 0.08& 0.01& 0.01& 0.01& 0.05& 0.01& 0.01& 0.01& 0.2& 0.15& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.63& 0.01& 1& 0.19& 0.17& 0.01& 0.01& 0.95& 0.01& 0.65& 0.54& 0.01& 0.01& 0.45& 0.63& 0.2\\ \cline{2-20}
& max\_leaf\_nodes& None& 31& 43& 28& 29& 11& 48& 17& 25& 13& 25& 10& 31& 33& 47& 44& 14& 23\\ \cline{2-20}
& min\_samples\_split& 2& 2& 7& 13& 1& 9& 13& 1& 13& 6& 10& 4& 12& 19& 16& 17& 3& 13\\ \cline{2-20}
& min\_samples\_leaf& 1& 17& 18& 2& 20& 2& 18& 9& 6& 7& 11& 17& 19& 8& 17& 3& 13& 9\\ \cline{2-20}
& n\_estimators& 100& 76& 64& 62& 141& 91& 67& 57& 104& 70& 67& 56& 59& 97& 81& 140& 85& 92\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of pd}
\end{figure*}

%%%%parameters for pf %%%%%%
\begin{figure*}[!ht]
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.53& 0.71& 0.37& 0.23& 0.67& 1& 1& 0.48& 0.97& 0.81& 1& 0.98& 0.92& 0.93& 0.98& 0.5& 0.99\\ \cline{2-20}
& infoPrune& 0.33& 0.68& 0.97& 0.43& 0.01& 0.22& 1& 0.76& 0.48& 0.61& 0.23& 0.04& 0.92& 0.59& 0.41& 0.88& 0.9& 0.23\\ \cline{2-20}
& min\_sample\_size& 4& 3& 1& 2& 1& 6& 4& 3& 5& 3& 9& 7& 3& 3& 8& 7& 2& 9\\ \cline{2-20}
& min\_Size& 0.5& 0.07& 0.03& 0.36& 0.06& 0.21& 0.38& 0.15& 0.19& 0.29& 0.08& 0.35& 0.24& 0.38& 0.67& 0.01& 0.25& 0.58\\ \cline{2-20}
& wriggle& 0.2& 0.91& 0.97& 0.47& 0.96& 0.82& 0.11& 0.37& 0.37& 0.06& 0.68& 0.23& 0.01& 0.51& 0.79& 0.53& 0.05& 0.08\\ \cline{2-20}
& depthMin& 2& 4& 1& 3& 3& 1& 1& 3& 4& 2& 3& 3& 1& 1& 1& 1& 3& 1\\ \cline{2-20}
& depthMax& 10& 10& 15& 7& 4& 14& 3& 15& 16& 15& 18& 6& 6& 5& 18& 10& 6& 16\\ \cline{2-20}
& wherePrune& False& True& True& False& True& True& True& True& True& True& False& True& True& True& True& True& True& False\\ \cline{2-20}
& treePrune& True& True& False& True& False& False& True& True& False& False& False& False& True& False& False& False& True& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 1& 1& 0.96& 0.88& 1& 1& 0.99& 0.88& 1& 0.83& 1& 1& 0.92& 0.9& 1& 1& 1\\ \cline{2-20}
& max\_feature& None& 0.01& 1& 0.93& 0.58& 0.01& 0.73& 1& 0.44& 0.01& 0.88& 0.01& 0.38& 0.48& 0.65& 0.86& 0.28& 0.01\\ \cline{2-20}
& min\_samples\_split& 2& 4& 4& 18& 3& 14& 19& 14& 16& 19& 12& 6& 2& 9& 8& 3& 6& 16\\ \cline{2-20}
& min\_samples\_leaf& 1& 12& 16& 19& 18& 1& 2& 5& 8& 8& 1& 10& 6& 12& 12& 13& 3& 10\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.89& 0.58& 0.88& 0.86& 1& 1& 1& 1& 1& 1& 1& 1& 0.78& 0.73& 1& 1& 0.93\\ \cline{2-20}
& max\_feature& None& 0.47& 0.04& 0.12& 0.38& 0.96& 0.87& 0.11& 0.01& 1& 0.16& 0.85& 0.99& 0.78& 0.77& 0.01& 0.35& 0.23\\ \cline{2-20}
& max\_leaf\_nodes& None& 35& 37& 38& 23& 13& 34& 36& 29& 10& 10& 10& 10& 33& 49& 50& 24& 37\\ \cline{2-20}
& min\_samples\_split& 2& 18& 10& 5& 16& 1& 20& 2& 1& 10& 5& 11& 5& 16& 4& 5& 19& 19\\ \cline{2-20}
& min\_samples\_leaf& 1& 16& 11& 6& 13& 2& 4& 2& 2& 2& 19& 6& 2& 4& 14& 2& 3& 18\\ \cline{2-20}
& n\_estimators& 100& 103& 95& 76& 88& 68& 88& 136& 90& 144& 115& 150& 99& 110& 114& 53& 108& 99\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of pf}
\end{figure*}

%%%%parameters for prec %%%%%%
\begin{figure*}[!ht]
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.53& 0.48& 0.41& 0.35& 0.88& 1& 1& 0.9& 0.96& 0.57& 1& 1& 0.56& 0.57& 0.8& 0.26& 0.65\\ \cline{2-20}
& infoPrune& 0.33& 0.68& 0.74& 0.31& 0.45& 0.78& 0.31& 0.53& 0.85& 0.04& 0.73& 0.54& 0.15& 1& 0.98& 0.23& 0.9& 0.19\\ \cline{2-20}
& min\_sample\_size& 4& 3& 6& 5& 2& 1& 5& 7& 1& 7& 5& 2& 8& 1& 1& 1& 2& 2\\ \cline{2-20}
& min\_Size& 0.5& 0.07& 0.23& 0.2& 0.21& 0.25& 0.54& 0.18& 0.36& 0.28& 0.51& 1.0& 0.33& 0.5& 0.84& 0.83& 0.04& 0.21\\ \cline{2-20}
& wriggle& 0.2& 0.91& 0.77& 0.58& 0.85& 0.17& 0.66& 0.33& 0.88& 0.13& 0.72& 0.18& 0.07& 0.43& 0.63& 0.74& 0.18& 0.75\\ \cline{2-20}
& depthMin& 2& 4& 2& 5& 2& 4& 2& 2& 2& 4& 2& 3& 4& 1& 5& 1& 2& 1\\ \cline{2-20}
& depthMax& 10& 10& 14& 6& 13& 7& 16& 15& 14& 13& 19& 16& 9& 16& 14& 11& 13& 15\\ \cline{2-20}
& wherePrune& False& True& False& True& True& True& True& True& True& True& True& True& True& True& True& False& True& False\\ \cline{2-20}
& treePrune& True& True& True& True& True& True& True& False& False& False& True& False& True& True& False& False& False& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.76& 0.99& 0.86& 0.48& 1& 1& 1& 0.71& 0.62& 0.65& 1& 0.95& 0.64& 0.5& 1& 0.99& 1\\ \cline{2-20}
& max\_feature& None& 0.09& 0.13& 0.05& 0.01& 0.01& 0.47& 0.01& 0.1& 0.63& 0.62& 0.44& 0.27& 0.28& 0.04& 0.75& 0.96& 0.21\\ \cline{2-20}
& min\_samples\_split& 2& 4& 19& 9& 9& 17& 14& 14& 16& 14& 12& 17& 3& 10& 12& 20& 13& 6\\ \cline{2-20}
& min\_samples\_leaf& 1& 15& 17& 8& 7& 1& 20& 1& 9& 12& 15& 10& 13& 7& 10& 4& 7& 20\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.92& 0.99& 0.71& 0.7& 1& 0.82& 1& 1& 1& 0.96& 0.73& 1& 0.76& 0.33& 1& 1& 0.98\\ \cline{2-20}
& max\_feature& None& 0.23& 0.13& 0.46& 0.69& 0.37& 0.56& 0.71& 0.01& 1& 0.01& 0.85& 0.48& 0.34& 0.02& 0.01& 0.08& 0.62\\ \cline{2-20}
& max\_leaf\_nodes& None& 12& 49& 23& 39& 10& 17& 20& 10& 10& 44& 37& 18& 35& 11& 31& 35& 28\\ \cline{2-20}
& min\_samples\_split& 2& 18& 8& 14& 1& 11& 3& 2& 1& 4& 14& 2& 1& 13& 8& 18& 2& 13\\ \cline{2-20}
& min\_samples\_leaf& 1& 11& 5& 11& 3& 2& 4& 20& 2& 2& 10& 3& 7& 7& 15& 6& 2& 9\\ \cline{2-20}
& n\_estimators& 100& 130& 146& 66& 96& 50& 50& 136& 84& 83& 129& 51& 150& 99& 58& 88& 85& 61\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of prec}
\end{figure*}

>>>>

 \setlength{\floatsep}{1ex}
 \setlength{\textfloatsep}{1ex}
 \newcommand{\subparagraph}{}

\usepackage[compact,small]{titlesec}
\DeclareMathSizes{7}{7}{7}{7} 
\pagenumbering{arabic}
\setlength{\columnsep}{7mm}

@@

\subsection{Implications}

time for an end to era of data mining in se? moving on to a new phase of learning-as-optimization

1) learning is actually an optimization tasks (e.g. see fig2 of  learners climbing the roc curve hill in http://goo.gl/x2EaAm)

2) our learners are all contorted to do some tasks X (e.g. minimize expected value of entropy), then we assess them on score Y (recall). which is nuts. maybe we should build the goal predicate into the learner (e.g http://menzies.us/pdf/10which.pdf)

3) given 1 + 2, maybe the whole paradigm of optimizing param selection is wrong. maybe what we need is a library of bees buzzing around making random choices (e.g. about descritziation) which other bees use, plus their own random choices (e.g. max depth of tree learned from discretized data) which is used by other bees, plus their own random choices (e.g. business users reading the models).  the funky thing here is that it can take some time before some of the bees (the discretizers) get feedback from the community of people using their decision (the tree learners).

@@

%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
\renewcommand\arraystretch{1.2}
\begin{figure*}[t!]
\renewcommand{\baselinestretch}{0.7}
\scriptsize
  \centering
	\begin{tabular}{|c|c|c|c|l|}
	\cline{1-5}
	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
\multicolumn{1}{c|}{Description} \\ \hline
	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
	& infogain & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
one is for clustering and the second one is building prediction model. we explicitly call Where-
clustering tree and CART tree, respectively}. \\ \cline{2-5} 
	 & min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
CART tree. \\ \cline{2-5} 
	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
\end{tabular} \\ \cline{2-5} 
    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
clustering tree. \\ \cline{2-5} 
	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
\hline
\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
split. \\ \cline{2-5}

@@

%%%%parameters for pd %%%%%%
\begin{figure*}[!t]

\renewcommand{\baselinestretch}{0.7}
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.17& 0.17& 0.02& 0.04& 0.42& 0.7& 0.8& 0.25& 0.32& 0.13& 0.61& 0.77& 0.09& 0.02& 0.68& 0.17& 0.01\\ \cline{2-20}
& infoPrune& 0.33& 0.13& 0.06& 0.12& 0.35& 0.44& 0.26& 0.33& 0.81& 0.03& 0.32& 0.89& 0.05& 0.1& 0.97& 0.15& 0.24& 0.01\\ \cline{2-20}
& min\_sample\_size& 4& 5& 2& 4& 1& 7& 6& 9& 6& 9& 8& 1& 3& 3& 9& 5& 4& 2\\ \cline{2-20}
& min\_Size& 0.5& 0.49& 0.24& 0.41& 0.26& 0.12& 0.03& 0.26& 0.06& 0.19& 0.38& 0.02& 0.07& 0.2& 0.2& 0.32& 0.13& 0.86\\ \cline{2-20}
& wriggle& 0.2& 0.65& 0.19& 0.42& 0.37& 0.22& 0.56& 0.64& 0.26& 0.79& 0.97& 0.23& 0.52& 0.99& 0.78& 0.15& 0.58& 0.55\\ \cline{2-20}
& depthMin& 2& 4& 3& 2& 5& 5& 4& 3& 5& 4& 4& 2& 4& 2& 1& 4& 3& 1\\ \cline{2-20}
& depthMax& 10& 16& 7& 19& 11& 14& 16& 12& 12& 19& 17& 12& 13& 15& 13& 3& 17& 15\\ \cline{2-20}
& wherePrune& False& True& False& False& False& False& False& False& True& True& False& False& True& False& True& False& False& False\\ \cline{2-20}
& treePrune& True& True& True& True& False& False& False& False& False& True& True& False& False& True& False& False& True& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.01& 0.13& 0.01& 0.01& 0.06& 0.34& 0.01& 0.15& 0.39& 0.01& 0.05& 0.06& 0.01& 0.01& 0.18& 0.06& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.9& 0.01& 0.01& 0.45& 0.14& 0.52& 0.57& 0.76& 1& 0.68& 0.01& 0.33& 0.01& 0.73& 0.04& 0.01\\ \cline{2-20}
& min\_samples\_split& 2& 17& 20& 7& 18& 9& 11& 15& 16& 12& 11& 2& 6& 3& 13& 19& 13& 10\\ \cline{2-20}
& min\_samples\_leaf& 1& 11& 1& 9& 2& 19& 14& 6& 15& 4& 17& 19& 9& 12& 5& 4& 7& 13\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.09& 0.01& 0.01& 0.01& 0.36& 0.49& 0.08& 0.01& 0.01& 0.01& 0.05& 0.01& 0.01& 0.01& 0.2& 0.15& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.63& 0.01& 1& 0.19& 0.17& 0.01& 0.01& 0.95& 0.01& 0.65& 0.54& 0.01& 0.01& 0.45& 0.63& 0.2\\ \cline{2-20}
& max\_leaf\_nodes& None& 31& 43& 28& 29& 11& 48& 17& 25& 13& 25& 10& 31& 33& 47& 44& 14& 23\\ \cline{2-20}
& min\_samples\_split& 2& 2& 7& 13& 1& 9& 13& 1& 13& 6& 10& 4& 12& 19& 16& 17& 3& 13\\ \cline{2-20}
& min\_samples\_leaf& 1& 17& 18& 2& 20& 2& 18& 9& 6& 7& 11& 17& 19& 8& 17& 3& 13& 9\\ \cline{2-20}
& n\_estimators& 100& 76& 64& 62& 141& 91& 67& 57& 104& 70& 67& 56& 59& 97& 81& 140& 85& 92\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of pd}
\end{figure*}

%%%%parameters for pf %%%%%%
\begin{figure*}[!t]

\renewcommand{\baselinestretch}{0.7}
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.53& 0.71& 0.37& 0.23& 0.67& 1& 1& 0.48& 0.97& 0.81& 1& 0.98& 0.92& 0.93& 0.98& 0.5& 0.99\\ \cline{2-20}
& infoPrune& 0.33& 0.68& 0.97& 0.43& 0.01& 0.22& 1& 0.76& 0.48& 0.61& 0.23& 0.04& 0.92& 0.59& 0.41& 0.88& 0.9& 0.23\\ \cline{2-20}
& min\_sample\_size& 4& 3& 1& 2& 1& 6& 4& 3& 5& 3& 9& 7& 3& 3& 8& 7& 2& 9\\ \cline{2-20}
& min\_Size& 0.5& 0.07& 0.03& 0.36& 0.06& 0.21& 0.38& 0.15& 0.19& 0.29& 0.08& 0.35& 0.24& 0.38& 0.67& 0.01& 0.25& 0.58\\ \cline{2-20}
& wriggle& 0.2& 0.91& 0.97& 0.47& 0.96& 0.82& 0.11& 0.37& 0.37& 0.06& 0.68& 0.23& 0.01& 0.51& 0.79& 0.53& 0.05& 0.08\\ \cline{2-20}
& depthMin& 2& 4& 1& 3& 3& 1& 1& 3& 4& 2& 3& 3& 1& 1& 1& 1& 3& 1\\ \cline{2-20}
& depthMax& 10& 10& 15& 7& 4& 14& 3& 15& 16& 15& 18& 6& 6& 5& 18& 10& 6& 16\\ \cline{2-20}
& wherePrune& False& True& True& False& True& True& True& True& True& True& False& True& True& True& True& True& True& False\\ \cline{2-20}
& treePrune& True& True& False& True& False& False& True& True& False& False& False& False& True& False& False& False& True& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 1& 1& 0.96& 0.88& 1& 1& 0.99& 0.88& 1& 0.83& 1& 1& 0.92& 0.9& 1& 1& 1\\ \cline{2-20}
& max\_feature& None& 0.01& 1& 0.93& 0.58& 0.01& 0.73& 1& 0.44& 0.01& 0.88& 0.01& 0.38& 0.48& 0.65& 0.86& 0.28& 0.01\\ \cline{2-20}
& min\_samples\_split& 2& 4& 4& 18& 3& 14& 19& 14& 16& 19& 12& 6& 2& 9& 8& 3& 6& 16\\ \cline{2-20}
& min\_samples\_leaf& 1& 12& 16& 19& 18& 1& 2& 5& 8& 8& 1& 10& 6& 12& 12& 13& 3& 10\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.89& 0.58& 0.88& 0.86& 1& 1& 1& 1& 1& 1& 1& 1& 0.78& 0.73& 1& 1& 0.93\\ \cline{2-20}
& max\_feature& None& 0.47& 0.04& 0.12& 0.38& 0.96& 0.87& 0.11& 0.01& 1& 0.16& 0.85& 0.99& 0.78& 0.77& 0.01& 0.35& 0.23\\ \cline{2-20}
& max\_leaf\_nodes& None& 35& 37& 38& 23& 13& 34& 36& 29& 10& 10& 10& 10& 33& 49& 50& 24& 37\\ \cline{2-20}
& min\_samples\_split& 2& 18& 10& 5& 16& 1& 20& 2& 1& 10& 5& 11& 5& 16& 4& 5& 19& 19\\ \cline{2-20}
& min\_samples\_leaf& 1& 16& 11& 6& 13& 2& 4& 2& 2& 2& 19& 6& 2& 4& 14& 2& 3& 18\\ \cline{2-20}
& n\_estimators& 100& 103& 95& 76& 88& 68& 88& 136& 90& 144& 115& 150& 99& 110& 114& 53& 108& 99\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of pf}
\end{figure*}

%%%%parameters for prec %%%%%%
\begin{figure*}[!ht]

\renewcommand{\baselinestretch}{0.7}
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.53& 0.48& 0.41& 0.35& 0.88& 1& 1& 0.9& 0.96& 0.57& 1& 1& 0.56& 0.57& 0.8& 0.26& 0.65\\ \cline{2-20}
& infoPrune& 0.33& 0.68& 0.74& 0.31& 0.45& 0.78& 0.31& 0.53& 0.85& 0.04& 0.73& 0.54& 0.15& 1& 0.98& 0.23& 0.9& 0.19\\ \cline{2-20}
& min\_sample\_size& 4& 3& 6& 5& 2& 1& 5& 7& 1& 7& 5& 2& 8& 1& 1& 1& 2& 2\\ \cline{2-20}
& min\_Size& 0.5& 0.07& 0.23& 0.2& 0.21& 0.25& 0.54& 0.18& 0.36& 0.28& 0.51& 1.0& 0.33& 0.5& 0.84& 0.83& 0.04& 0.21\\ \cline{2-20}
& wriggle& 0.2& 0.91& 0.77& 0.58& 0.85& 0.17& 0.66& 0.33& 0.88& 0.13& 0.72& 0.18& 0.07& 0.43& 0.63& 0.74& 0.18& 0.75\\ \cline{2-20}
& depthMin& 2& 4& 2& 5& 2& 4& 2& 2& 2& 4& 2& 3& 4& 1& 5& 1& 2& 1\\ \cline{2-20}
& depthMax& 10& 10& 14& 6& 13& 7& 16& 15& 14& 13& 19& 16& 9& 16& 14& 11& 13& 15\\ \cline{2-20}
& wherePrune& False& True& False& True& True& True& True& True& True& True& True& True& True& True& True& False& True& False\\ \cline{2-20}
& treePrune& True& True& True& True& True& True& True& False& False& False& True& False& True& True& False& False& False& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.76& 0.99& 0.86& 0.48& 1& 1& 1& 0.71& 0.62& 0.65& 1& 0.95& 0.64& 0.5& 1& 0.99& 1\\ \cline{2-20}
& max\_feature& None& 0.09& 0.13& 0.05& 0.01& 0.01& 0.47& 0.01& 0.1& 0.63& 0.62& 0.44& 0.27& 0.28& 0.04& 0.75& 0.96& 0.21\\ \cline{2-20}
& min\_samples\_split& 2& 4& 19& 9& 9& 17& 14& 14& 16& 14& 12& 17& 3& 10& 12& 20& 13& 6\\ \cline{2-20}
& min\_samples\_leaf& 1& 15& 17& 8& 7& 1& 20& 1& 9& 12& 15& 10& 13& 7& 10& 4& 7& 20\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.92& 0.99& 0.71& 0.7& 1& 0.82& 1& 1& 1& 0.96& 0.73& 1& 0.76& 0.33& 1& 1& 0.98\\ \cline{2-20}
& max\_feature& None& 0.23& 0.13& 0.46& 0.69& 0.37& 0.56& 0.71& 0.01& 1& 0.01& 0.85& 0.48& 0.34& 0.02& 0.01& 0.08& 0.62\\ \cline{2-20}
& max\_leaf\_nodes& None& 12& 49& 23& 39& 10& 17& 20& 10& 10& 44& 37& 18& 35& 11& 31& 35& 28\\ \cline{2-20}
& min\_samples\_split& 2& 18& 8& 14& 1& 11& 3& 2& 1& 4& 14& 2& 1& 13& 8& 18& 2& 13\\ \cline{2-20}
& min\_samples\_leaf& 1& 11& 5& 11& 3& 2& 4& 20& 2& 2& 10& 3& 7& 7& 15& 6& 2& 9\\ \cline{2-20}
& n\_estimators& 100& 130& 146& 66& 96& 50& 50& 136& 84& 83& 129& 51& 150& 99& 58& 88& 85& 61\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of prec}
\end{figure*}

%%%%parameters for F %%%%%%
\begin{figure*}[!ht]
